Orientation Control System: Enhancing Aerial Maneuvers \\ for Quadruped Robots

### 2022-10-27 humanoids22roscia.tex
bibliography backend and starting comments of reviewers

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

@@

%\documentclass[journal,letterpaper]{IEEEtran}
% include the list of acronyms, math commands and new commands used in this paper
\input{includes/used_packages.tex}
\input{includes/acronyms.tex}
\input{includes/math_commands.tex}
\input{includes/newcommands.tex}
\hypersetup{draft}
\makeglossaries

@@

\subsection{Outline}
The reminder of this paper is organized as follow. In Section \ref{sec:background}, the law of conservation of the total angular momentum is recalled. In Section \ref{sec:ocs}, the design principles are presented together with the strategy for simultaneously control the robot roll and pitch orientations. Section \ref{sec:simulations} presents simulation in different scenarios that demonstrate the the capability of our \gls{ocs} to reject disturbances and to track angular references when there is no contact with the ground, and damping of base oscillation after the touch-down. Conclusions and a possible evolution of the work ar reported in Section \ref{sec:conclusions}.
%

@@

\section{Orientation Control System}
\label{sec:ocs}
In this section, we present a procedure to select the inertia of the flywheels, and we show how to exploit them for simultaneously controlling the robot roll and pitch orientation.
\subsection{Inertia Selection}
A preliminary analysis for the selection of the flywheels' inertia can be performed with the Elroy's Beanie model, depicted in Fig. \ref{fig:elroy-beanie}.
\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{figures/elroys-beanie.eps}
	\caption{\small Schematic representation of the Elroy's Beanie model used for the preliminary analysis of the pitch motion.}
	\label{fig:elroy-beanie}
\end{figure} 
This consists of two rigid bodies connected through their \gls{com} with a revolute joint. One of the bodies represents the robot in its nominal configuration. The other models the \gls{ocs}, here represented by a single wheel for the sake of simplicity. The aim is to examine the rotational dynamics of the system as a whole. To simplify the analysis, in the following we will refer only to the effects on the pitch angle of the robot, keeping in mind that the same arguments apply also to the roll. 
Let us identify the moment of inertia of the robot in the nominal configuration as $I_r$ and the moment of inertia of the two flywheels as $I_f$, both referred to the system \gls{com}.
The angular momentum $L$ of this system can be written as
\begin{equation}\label{eq:ang_mom_elroy}
L(t) = \left(I_r + I_{f}\right)\dot{\theta}(t) + I_{f}\dot{\gamma}(t)
\end{equation}
where $\dot{\theta}$ and $\dot{\gamma}$ are respectively the robot pitch rate and the angular speed of the wheel.
We want to drive the robot to a desired pitch rate $\dot{\theta}_{des}$ by acting on the wheel speed.
Without loss of generality, we can assume the flywheel is stationary with the robot at the instant at which the reorientation maneuver starts ($\dot{\gamma}_0 = 0$), having a system angular momentum of $L_0 = \left(I_r + I_{f}\right)\dot{\theta}_0$.
Under the condition of conservation of the angular momentum, this quantity is constant over time and it is possible to estimate the lower bound for $I_{f}$ given a desired pitch rate and the maximum velocity of the flywheels $\dot{\gamma}_{max}$:
\begin{equation}
I_{f} \geq I_r \dfrac{ \Delta \dot{\theta} }{\Delta \dot{\theta}+\dot{\gamma}_{max}}.
\end{equation}
where $\Delta \dot{\theta} =  \left\lvert \dot{\theta}_0-\dot{\theta}_{des} \right\rvert$ is the base velocity variation.
Fig. \ref{fig:inertia_limits} reports the lower bound of $I_{f}$ given the desired base velocity variation and the maximum velocity of the actuator.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figures/lowerbound.eps}
	\caption{\small Minimum inertia of the \gls{ocs} (normalized by the robot inertia) necessary to achieve a base velocity variation $\Delta \dot{\theta}$, given the actuation bound $\dot \gamma^{max}$.}
	\label{fig:inertia_limits}
\end{figure}

@@

In the second test, we demonstrate the ability of the \gls{ocs} to reorient the base.
We let the robot fall from a height of $1 \ \mathrm{m}$ with an initial pitch orientation of $30^\circ$ and zero base angular velocity.
If we do not actuate the flywheels, the robot touches the ground with the same initial orientation and the trunk oscillates. If the \gls{ocs}is enabled, it drives the robot base to be horizontal when it is still in the air and the oscillations after the touch-down are drastically reduced, both in the pitch angle and forward direction (Fig. \ref{fig:fall_plot}).
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{figures/fall_plot.eps}
	\caption{\small Second Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. The \gls{ocs} drives the robot orientation during a fall to be horizontal. This allows to damp for damping the base oscillations after the touch-down (vertical dashed line), even without implementing a landing strategy}
	\label{fig:fall_plot}
\end{figure}

@@

\printbibliography
\end{document}

>>>>

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}      % Use this line for a4 paper

@@

% these commands are needed because we use ieeeconf with natbib
\let\labelindent\relax

\makeatletter
\let\NAT@parse\undefined
\makeatother

% include the list of acronyms, math commands and new commands used in this paper
\input{includes/used_packages.tex}
\input{includes/acronyms.tex}
\input{includes/math_commands.tex}
\input{includes/newcommands.tex}
\hypersetup{draft}
\makeglossaries

@@

\subsection{Outline}
The remainder of this paper is organized as follow. In Section \ref{sec:background}, the law of conservation of the total angular momentum is recalled. In Section \ref{sec:ocs}, the design principles are presented together with the strategy for simultaneously control the robot roll and pitch orientations. Section \ref{sec:simulations} presents simulation in different scenarios that demonstrate the the capability of our \gls{ocs} to reject disturbances and to track angular references when there is no contact with the ground, and damping of base oscillation after the touch-down. Conclusions and a possible evolution of the work ar reported in Section \ref{sec:conclusions}.
%

@@

\FR{In Solo12, even if the each limb accounts for about $13.4\%$ of the total mass, changes of the total robot inertia come with the motion of only the upperleg (thigh) and the lowerleg (calf), since the displacement of distribution of the hip mass with the system \acrshort{com} is approximately constant. In view of this, each limb accounts for only $7.5\%$ of the total mass in varying the the total robot inertia.}

\section{Orientation Control System}
\label{sec:ocs}
In this section, we present a procedure to select the inertia of the flywheels, and we show how to exploit them for simultaneously controlling the robot roll and pitch orientation.
\subsection{Bounds on the Inertia}
A preliminary analysis for the selection of the flywheels' inertia can be performed with the Elroy's Beanie model, depicted in Fig. \ref{fig:elroy-beanie}.
\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{figures/elroys-beanie.eps}
	\caption{\small Schematic representation of the Elroy's Beanie model used for the preliminary analysis of the pitch motion.}
	\label{fig:elroy-beanie}
\end{figure} 
This consists of two rigid bodies connected through their \gls{com} with a revolute joint. One of the bodies represents the robot in its nominal configuration. The other models the \gls{ocs}, here represented by a single wheel for the sake of simplicity. The aim is to examine the rotational dynamics of the system as a whole. To simplify the analysis, in the following we will refer only to the effects on the pitch angle of the robot, keeping in mind that the same arguments apply also to the roll. 
Let us identify the moment of inertia of the robot in the nominal configuration as $I_r$ and the moment of inertia of the two flywheels as $I_f$, both referred to the system \gls{com}.
The angular momentum $L$ of this system can be written as
\begin{equation}\label{eq:ang_mom_elroy}
L(t) = \left(I_r + I_{f}\right)\dot{\theta}(t) + I_{f}\dot{\gamma}(t)
\end{equation}
where $\dot{\theta}$ and $\dot{\gamma}$ are respectively the robot pitch rate and the angular speed of the wheel.
We want to drive the robot to a desired pitch rate $\dot{\theta}_{des}$ by acting on the wheel speed.
Without loss of generality, we can assume the flywheel is stationary with the robot at the instant at which the reorientation maneuver starts ($\dot{\gamma}_0 = 0$), having a system angular momentum of $L_0 = \left(I_r + I_{f}\right)\dot{\theta}_0$.
Under the condition of conservation of the angular momentum, this quantity is constant over time and it is possible to estimate the lower bound for $I_{f}$ given a desired pitch rate and the maximum velocity of the flywheels $\dot{\gamma}_{max}$:
\begin{equation}
I_{f} \geq I_r \dfrac{ \Delta \dot{\theta} }{\Delta \dot{\theta}+\dot{\gamma}_{max}}.
\end{equation}
where $\Delta \dot{\theta} =  \left\lvert \dot{\theta}_0-\dot{\theta}_{des} \right\rvert$ is the base velocity variation.
Fig. \ref{fig:inertia_limits} reports the lower bound of $I_{f}$ given the desired base velocity variation and the maximum velocity of the actuator.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figures/lowerbound.eps}
	\caption{\small Minimum inertia of the \gls{ocs} (normalized by the robot inertia) necessary to achieve a base velocity variation $\Delta \dot{\theta}$, given the actuation bound $\dot \gamma^{max}$.}
	\label{fig:inertia_limits}
\end{figure}

@@

In the second test, we demonstrate the ability of the \gls{ocs} to reorient the base.
We let the robot fall from a height of $1 \ \mathrm{m}$ with an initial pitch orientation of $30^\circ$ and zero base angular velocity.
If we do not actuate the flywheels, the robot touches the ground with the same initial orientation and the trunk oscillates. If the \gls{ocs} is enabled, it drives the robot base to be horizontal when it is still in the air and the oscillations after the touch-down are drastically reduced, both in the pitch angle and forward direction (Fig. \ref{fig:fall_plot}).
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{figures/fall_plot.eps}
	\caption{\small Second Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. The \gls{ocs} drives the robot orientation during a fall to be horizontal. This allows to damp for damping the base oscillations after the touch-down (vertical dashed line), even without implementing a landing strategy}
	\label{fig:fall_plot}
\end{figure}

@@

\bibliography{references/bibliography}
%\printbibliography
\end{document}
